The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-02-03 docs/language_constraint.tex
a little more editing

\isection{Surface Analysis.}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). 
\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings.
\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). 
\yc{Again, any cogsci literature on this?} \nascomment{feels
  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.

>>>>

\isection{Surface Analysis.}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). This is inline with findings by \citet{yanchevaautomatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive. Furthermore, \citet{buller1996interpersonal} suggests lying increases one's cognitive load, which in turn could affect sentence length.
%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings. 
\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
% The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.
Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones. \ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, is there anything there?}.
Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). This is in line with previous findings that dececptively written text expresses more negative emotion compared to truthful text \cite{Newman:2003}.
%\yc{Again, any cogsci literature on this?} \nascomment{feels
%  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.
